Supplementary Material for Asymmetry paper

### 2020-05-01 Supplementary/Sup_mat.Rmd
updated sup mat

df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p,
             colour = diff)) + 
  geom_line() + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")
```

>>>>

df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p)) + 
  geom_histogram(data = df_part2, 
                 aes(x = (norm_pos + 1)/2,
                     y = ..density..),
                 binwidth = .1,
                 colour = "blue",
                 fill = "blue",
                 alpha = .2) + 
  geom_line(aes(colour = diff)) + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")
```
